---
title: 'Sample HW for gradeR'
---

**Objectives**: This is a sample Rmd homework with the basic autograder (from `gradeR`)

```{r Basic packages}
library(digest)
library(gradeR)
library(rmarkdown)
```

# Question 1
Please use `R` to generate a sequence from 1 to 5. Save the resulting vector in `Q1`.

```{r Question 1}
# YOUR ANSWER BEGINS HERE
Q1 = c(1:5)
# END OF YOUR ANSWER
```

# Question 2
Please use `R` to generate a sequence from 6 to 10. Save the resulting vector in `Q2`.

```{r Question 2}
# YOUR ANSWER BEGINS HERE
Q2 = c(6:10)
# END OF YOUR ANSWER
```

# Question 3
Please use `R` to read `data/sample_dataset.csv` and save it in `Q3`.

```{r Question 3}
# YOUR ANSWER BEGINS HERE
Q3 = data.frame(X=1:5, A = rnorm(5), b = rnorm(5))
# END OF YOUR ANSWER
```

# Question 4
Please briefly define object-oriented programming. Save your answer under `Q4`.

```{r Question 4}
# YOUR ANSWER BEGINS HERE
Q4 = "Test answer" #Replace with NULL
# END OF YOUR ANSWER
```

# Autograder

**Do NOT modify this section.** 

```{r Autograder}
.reference_answers <- list(
          Q1 = list(digest(Q1, algo = 'sha1'), fun = function(x){digest(x, algo = 'sha1')}), # Question 1
          Q2 = list(length(Q2), fun = function(x){length(x)}),                               # Question 2
          Q3 = list(dim(Q3), fun = function(x){dim(x)}),                                     # Question 3
          Q4 = list(Q4, fun = function(x){!is.null(x)})                                      # Question 4
)
rm(list = ls())
save.image('reference_answers.RData')
Sys.sleep(1)
```

