---
title: "Creating an assignment with gradeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating an assignment with gradeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(gradeR)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The `gradeR` is able to generate automatic templates for more complex assignments. These templates are designed as GitHub repositories to be released using GitHub classroom. Now, let's asumme that you're interested in creating all the basic files that are needed for `gradeR` to work for you as an instructor and your students. Note that students will have access to the autograder at any time. However, answers will be either (1) encrypted and saved in a hidden object in the environment or (2) simply saved into a hidden object (also in the environment). Instructors can decide when to encrypt answers. 

# 1. Homework template

To create a template of the HW using `gradeR`, use the `homework_template()` function. This function will create two folders in your current working directory. First, the `data` folder, where the instructor is expected to provide any external datasets to the student. Second, a `tests` folder, where the instructor is going to (1) develop their Homework, and (2) store correct answers.

```{r eval=FALSE}
homework_template()
```

# 2. Modify the template

Now, it's time for the instructor to make changes to the `tests/1_answers_template.Rmd` file. Note that `gradeR` has already rendered the same file into `1_answers_template.html`. The `tests/1_answers_template.Rmd`, which should be modified by the instructor, is expected to contain all the correct answers for each of the questions in the HW. The `tests/0_answers_template_original.Rmd` file should NEVER be modified and is used as a reference to the instructor. 

Unless you know what you are doing, **NEVER** modify the autograder section by hand. You can change anything before those lines. Final answers MUST be saved with the structure `QX = `, with `X` representing any number. Failing to follow that structure will cause the autograder to fail. Both the autograder section and the `QX = ` structure in final answers are the only two aspects that should NOT be modified.

You can render your `tests/1_answers_template.Rmd` file as many times as you need and troubleshoot with it until it renders appropriately and all the answers are shown as correct. 

Finally, note that a `README.rmd` file was created in the root of your working direct. The `README.rmd` should be used to present basic information to the students in the GitHub repo. Please make all the changes you need in the `README.rmd`. Do not modify lines of code below the autograder in the same file. 

# 3. Generate the student's markdown

Once your HW template is ready, you'll need to generate the relevant files for your students using the `generate_student()` function. This function will create a `0_Homework.Rmd` file, a blank template for your students to answer the questions. The autograder will be tested in a newly rendered `0_Homework.html` that was generated from `0_Homework.Rmd`. Finally, rendering the `0_Homework.Rmd` will always render the `README.Rmd`, which in turns create the `README.md` file.

```{r eval=FALSE}
generate_student()
```



# 4. Release the HW

Create a template repo in GitHub. Use GitHub classroom. Push only the relevant files (do NOT push the answers). I will talk more about how to encrypt R files later on.


# 5. After the HW is due

Clone the repositories using GitHub Classroom assistant.

```{r}
unlink(c('0_Homework.html',
'0_Homework.Rmd',
'data',
'README.md',
'README.Rmd',
'tests'), recursive = TRUE)
```







