---
title: "Quick introduction to gradeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick introduction to gradeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(gradeR)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Assume three of your students submitted their homework. One student didn't complete the questions, a second student submitted only wrong answers, and a third student answered all questions correctly:

```{r setup}
student_answers_no_answers <- list(
  Q1 = NULL, 
  Q2 = NULL, 
  Q3 = NULL,
  Q4 = NULL
)

student_answers_wrong <- list(
  Q1 = c(1:3), 
  Q2 = c(1:10), 
  Q3 = data.frame(1:2),
  Q4 = NULL
)

student_answers_right <- list(
  Q1 = c(1:5), 
  Q2 = c(6:10), 
  Q3 = data.frame(X=1:5, A = rnorm(5), b = rnorm(5)),
  Q4 = 'test'
)

Q1 = c(1:5)
Q2 = c(6:10)
Q3 = data.frame(X=1:5, A = rnorm(5), b = rnorm(5))
Q4 = 'test'
```

The instructor created their own autograder to grade these questions.. The autograder is a list of lists. The first level of the list will have as many elements as questions to grade. Each nested list contains only two elements. The first element is the correct answer. The second is the function that is used to transform the student's answer into a compatible answer.

```{r}
.reference_answers <- list(
  Q1 = list(digest(Q1, algo = 'sha1'), fun = function(x){digest(x, algo = 'sha1')}), # Question 1
  Q2 = list(length(Q2), fun = function(x){length(x)}),                               # Question 2
  Q3 = list(dim(Q3), fun = function(x){dim(x)}),                                     # Question 3
  Q4 = list(Q4, fun = function(x){!is.null(x)})                                      # Question 4
)
```

Let's now grade the submissions using `gradeR`:

```{r}
gradeR(student_answers = student_answers_no_answers, reference_answers = .reference_answers, maximum_grade=10)
gradeR(student_answers = student_answers_wrong, reference_answers = .reference_answers, maximum_grade=10)
gradeR(student_answers = student_answers_right, reference_answers = .reference_answers, maximum_grade=10)
```


